### Question 1
#### (a)i
```{r}
x<-c()
x[55:58]<-c(55,56,57,58)
qx<-c()
qx[55:57] <- c(0.001046, 0.001199,0.001375)
```
calculate the life table corresponding to these $q_x$ values
```{r}
lx<-c()
lx[55]<-100000
dx<-c()
for (i in 55:58) {
  dx[i]<-lx[i]*qx[i]
  lx[i+1]<-lx[i]-dx[i]
}
```
print the details
```{r}
table<-cbind(x[55:58],qx[55:58],lx[55:58])
colnames(table)<-c("x","qx","lx")
table
```
the increasing rate $i=1.92308\%$ and the interest on valuation basis is 6%
```{r}
i<-(1+0.06)/(1+0.0192308)-1
v<-1/(1+i)
d<-1-v
```
$${a}_{x+t\,\overline{n-t}|}=\frac{v-{A}_{x+t\,\overline{n-t}|}}{d}$$
```{r}
A<-c()
A[55:56]<- c(0.889132,0.924607)
a<-c()
a[55:56]<-(v-A[55:56])/d
a[55:56]
```
For this three year temporary annuities, need:
1.Premium
2.Expenses
3.Benefits
4.Policy values
```{r}
premium<-c()
premium[55:57]<-c(40250,0,0)
exp_i<-c()
exp_i[55:57]<-c(rep(0,3))
exp_i[55]<-100+0.015*premium[55]
exp_a<-c()
for (i in 55:57) {
  exp_a[i]<-10*(1+0.05)^(i-55)
}
benefit<-c()
for (i in 55:57) {
  benefit[i]<- 15000*(1+0.0192308)^(x[i]-55)
}
policyvalue<-c()
policyvalue[55:56]<-benefit[55:56]*a[55:56]
policyvalue[57]<-0
```
set a table
```{r}
table<-cbind(x[55:57],premium[55:57],exp_i[55:57],exp_a[55:57],benefit[55:57],policyvalue[55:57])
colnames(table)<-c("x","premium","expenses_i","expenses_a","benefit","policy value")
table
```
calculate enpected amoumt
1.Expected Premium
2.Expected Expenses
3.Expected Benefits
4.Expected Policy values
```{r}
Eprem<-c()
for (i in 55:57) {
  Eprem[i]<-premium[i]*lx[i]/lx[55]
}
Eexp_i<-c()
for (i in 55:57) {
  Eexp_i[i]<-exp_i[i]*lx[i]/lx[55]
}
Eexp_a<-c()
for (i in 55:57) {
  Eexp_a[i]<-exp_a[i]*lx[i]/lx[55]
}
Ebenefit<-c()
for (i in 55:57) {
  Ebenefit[i]<-benefit[i]*lx[i+1]/lx[55]
}
Epolicyvalue<-c()
for (i in 55:57) {
  Epolicyvalue[i]<-policyvalue[i]*lx[i+1]/lx[55]
}
interest<-c()
interest[55]<-0.08*(Eprem[55]-Eexp_i[55])
interest[56:57]<-0.08*(Eprem[56:57]+Epolicyvalue[55:56]-Eexp_i[56:57])
transfer<-c()
transfer[55]<-Eprem[55]+interest[55]-Eexp_a[55]-Eexp_i[55]-Epolicyvalue[55]-Ebenefit[55]
transfer[56:57]<-Eprem[56:57]+Epolicyvalue[55:56]+interest[56:57]-Eexp_a[56:57]-Eexp_i[56:57]-Epolicyvalue[56:57]-Ebenefit[56:57]
```
set a table
```{r}
table<-cbind(x[55:57],Eprem[55:57],Eexp_i[55:57],Eexp_a[55:57],Ebenefit[55:57],Epolicyvalue[55:57],interest[55:57],transfer[55:57])
colnames(table)<-c("x","Epremium","Eexpenses_i","Eexpenses_a","Ebenefit","Epolicy value","interest","transfer")
table
```
#### (a)ii
```{r}
sum<-sum(transfer[55:57]*1.12^(-c(1:3)))
sum
sum/Eprem[55]
```
#### (b)
```{r}
IRR<-function(p) sum((1+p)^(-c(1:3))*trnsfr_EOY[55:57])
uniroot(IRR,c(0.4,0.6))
```