### Question 2

#### (a)

#### front end load
the premium-based fee in the first year of 45% of premium exactly matches the initial expenses.

#### Double-decrement Table
$$q_w^30=1$$
```{r}
x<-c()
x[30:40]<-c(30:40)
q.x_d<-c()
q.x_d[30:39]<-c(0.00043,0.00042,0.00041,0.00040,0.00041,0.00042,0.00043,0.00045,0.00049,0.00053)
q.x_w<-c()
q.x_w[30:39]<-c(0.25,0.2,0.175,0.15,0.15,0.15,0.15,0.15,0.15,1)
```
set a table
```{r}
table<-cbind(x[30:39],q.x_d[30:39],q.x_w[30:39])
colnames(table)<-c("x","q.x_d","q.x_w")
table
```
calculate $$(aq)_d^x$$, $$(aq)_w^x$$
$$(aq)_d^x=q_d^x*(1-0.5q_w^x)$$, $$(aq)_w^x=q_w^x*(1-0.5q_d^x)$$
```{r}
aq.x_d<-q.x_d*(1-0.5*q.x_w)
aq.x_w<-q.x_w*(1-0.5*q.x_d)
table<-cbind(x[30:39],aq.x_d[30:39],aq.x_w[30:39])
colnames(table)<-c("x","aq.x_d","aq.x_w")
table
```
$$(al)_30=100000$$
```{r}
al.x<-c()
al.x[30]<-100000
ad.x_d<-c()
ad.x_w<-c()
for (i in 30:40) {
  ad.x_d[i]<-al.x[i]*aq.x_d[i]
  ad.x_w[i]<-al.x[i]*aq.x_w[i]
  al.x[i+1]<-al.x[i]-ad.x_d[i]-ad.x_w[i] 
}
table<-cbind(x[30:40],al.x[30:40],ad.x_d[30:40],ad.x_w[30:40])
colnames(table)<-c("x","al.x","ad.x_d","ad.x_w")
table
```
#### Calculating the Possible Amounts for an In-force Policy 
```{r}
i<-0.1
a<-c()
a[30:39]<-c(rep(0.99,10))
a[30]<-0.55
b<-0.005
m<-0.003
P<-c()
P[30:39]<-c(rep(5000,10))
IP<-P*a*(1-b)
VU<-c()
VU[30]<-IP[30]*(1+i)*(1-m)
for (j in 31:39) {
  VU[j]<-(VU[j-1]+IP[j])*(1+i)*(1-m)
}
table<-cbind(x[30:39],IP[30:39],VU[30:39])
colnames(table)<-c("x","Invested premium","Value of units at end of year")
table
```
#### Expected Amounts per Initial Policy for the Unit Fund 
```{r}
EIP<-c()
for (i in 30:39) {
  EIP[i]<-IP[i]*al.x[i]/al.x[30]
}
EVU<-c()
for (i in 30:39) {
  EVU[i]<-VU[i]*al.x[i+1]/al.x[30]
}
i<-0.1
interest<-c()
interest[30]<-EIP[30]*i
for (j in 31:39) {
  interest[j]<-i*(EVU[j-1]+EIP[j])
}
transfer<-c()
transfer[30]<-EIP[30]+interest[30]-EVU[30]
for (i in 31:39) {
  transfer[i]<-EVU[i-1]+EIP[i]+interest[i]-EVU[i]
}
table<-cbind(x[30:39],EIP[30:39],interest[30:39],EVU[30:39],transfer[30:39])
colnames(table)<-c("x","EIP","interest","EVU","transfer")
table
```
#### 
```{r}
fee<-P*(1-a)
margin<-P*a*b
expenses<-c()
expenses[30]<-5000*0.45+58
for (j in 31:39) {
  expenses[j]<- 58*(1+0.2)^(j-30)
}
BFT<-VU
table<-cbind(x[30:39],fee[30:39],margin[30:39],expenses[30:39],BFT[30:39])
colnames(table)<-c("x","fee","margin","expenses","BFT")
table
```
#### Expected Amounts per Initial Policy for the Non¨Cunit Fund 
```{r}
Efee<-c()
for (i in 30:39) {
  Efee[i]<-fee[i]*al.x[i]/al.x[30]
}
Emargin<-c()
for (i in 30:39) {
  Emargin[i]<-margin[i]*al.x[i]/al.x[30]
}
Eexpenses<-c()
for (i in 30:39) {
  Eexpenses[i]<-expenses[i]*al.x[i]/al.x[30]
}
Einterest<-c()
Einterest<-0.08*(Efee+Emargin-Eexpenses)
Edeathbenefit<-c()
for (i in 30:39) {
  Edeathbenefit[i]<-BFT[i]*ad.x_d[i]/al.x[30]
}
Esurrenderbenefit<-c()
for (i in 30:39) {
  Esurrenderbenefit[i]<-BFT[i]*ad.x_w[i]/al.x[30]
}
transfer_EOY<-c()
transfer_EOY<-Efee+Emargin-Eexpenses+Einterest-Edeathbenefit-Esurrenderbenefit+transfer
table<-cbind(x[30:39],Efee[30:39],Emargin[30:39],Eexpenses[30:39],Einterest[30:39],Edeathbenefit[30:39],Esurrenderbenefit[30:39],transfer_EOY[30:39])
colnames(table)<-c("x","Efee","Emargin","Eexpenses","Einterest","Edeathbenefit","Esurrenderbenefit","transfer_EOY")
table
```
#### Profitability 
PV of Transfers at 12.50%
```{r}
sum<-sum(transfer_EOY[30:39]*1.125^(-c(1:10)))
sum
sum/P[30]
```

#### (b)

find the changed policy value in year 9 to make the vaule of transfer in the final year is zero.

```{r}

find_policy_value <- function(target){
x<-c()
x[30:40]<-c(30:40)
q.x_d<-c()
q.x_d[30:39]<-c(0.00043,0.00042,0.00041,0.00040,0.00041,0.00042,0.00043,0.00045,0.00049,0.00053)
q.x_w<-c()
q.x_w[30:39]<-c(0.25,0.2,0.175,0.15,0.15,0.15,0.15,0.15,0.15,1)

## ------------------------------------------------------------------------
aq.x_d<-q.x_d*(1-0.5*q.x_w)
aq.x_w<-q.x_w*(1-0.5*q.x_d)

## ------------------------------------------------------------------------
al.x<-c()
al.x[30]<-100000
ad.x_d<-c()
ad.x_w<-c()
for (i in 30:40) {
  ad.x_d[i]<-al.x[i]*aq.x_d[i]
  ad.x_w[i]<-al.x[i]*aq.x_w[i]
  al.x[i+1]<-al.x[i]-ad.x_d[i]-ad.x_w[i] 
}


## ------------------------------------------------------------------------
i<-0.1
a<-c()
a[30:39]<-c(rep(0.99,10))
a[30]<-0.55
b<-0.005
m<-0.003
P<-c()
P[30:39]<-c(rep(5000,10))
IP<-P*a*(1-b)
VU<-c()
VU[30]<-IP[30]*(1+i)*(1-m)
for (j in 31:39) {
  VU[j]<-(VU[j-1]+IP[j])*(1+i)*(1-m)
}
VU[38]<-target


## ------------------------------------------------------------------------
EIP<-c()
for (i in 30:39) {
  EIP[i]<-IP[i]*al.x[i]/al.x[30]
}
EVU<-c()
for (i in 30:39) {
  EVU[i]<-VU[i]*al.x[i+1]/al.x[30]
}
i<-0.1
interest<-c()
interest[30]<-EIP[30]*i
for (j in 31:39) {
  interest[j]<-i*(EVU[j-1]+EIP[j])
}
transfer<-c()
transfer[30]<-EIP[30]+interest[30]-EVU[30]
for (i in 31:39) {
  transfer[i]<-EVU[i-1]+EIP[i]+interest[i]-EVU[i]
}


## ------------------------------------------------------------------------
fee<-P*(1-a)
margin<-P*a*b
expenses<-c()
expenses[30]<-5000*0.45+58
for (j in 31:39) {
  expenses[j]<- 58*(1+0.2)^(j-30)
}
BFT<-VU


## ------------------------------------------------------------------------
Efee<-c()
for (i in 30:39) {
  Efee[i]<-fee[i]*al.x[i]/al.x[30]
}
Emargin<-c()
for (i in 30:39) {
  Emargin[i]<-margin[i]*al.x[i]/al.x[30]
}
Eexpenses<-c()
for (i in 30:39) {
  Eexpenses[i]<-expenses[i]*al.x[i]/al.x[30]
}
Einterest<-c()
Einterest<-0.08*(Efee+Emargin-Eexpenses)
Edeathbenefit<-c()
for (i in 30:39) {
  Edeathbenefit[i]<-BFT[i]*ad.x_d[i]/al.x[30]
}
Esurrenderbenefit<-c()
for (i in 30:39) {
  Esurrenderbenefit[i]<-BFT[i]*ad.x_w[i]/al.x[30]
}
transfer_EOY<-c()
transfer_EOY<-Efee+Emargin-Eexpenses+Einterest-Edeathbenefit-Esurrenderbenefit+transfer
transfer_EOY[39]
}

uniroot(find_policy_value,c(60000,70000))
```

#### {c}
The vaule of transfer in the final year is zero. Unit fnd earning rate is 10%, lower than the discount rate (12.5%). Therefore, the expected present value decreases.